---
title: "COMP3359"
author: "Buntoro Reynard Verill & Andrianto Reno"
date: "3/11/2021"
output: 
  html_document:
    df_print: paged
    highlight: breezedark
    theme: cosmo
    toc: yes
    toc_float:
      collapsed: no
    css: assets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", out.width = "80%")
options(scipen = 99)
```


<style>
body {
text-align: justify}
</style>

# Objectives

In this project, we aim to implement a proper movie recommendation system for customers using the data frame provided by netflix back in 2005 for its prize competition. Here, we will supplement suitable data pre-processing methods, data explorations, and data visualizations to ultimately aid the readers of this report in understanding the work-flow of our project, which finally leads to the development of our models, complemented with various error analysis, and suggestions for improvements.

# Libraries

Firstly, we import some of the necessary packages for the development of our project and deployment of suitable models.

```{r cars}
library(tidyverse)
library(ggplot2)
library(plotly)
library(glue)
library(scales)
```

# Data Reading

In this section we will read the data into our IDE (i.e. in our case, to RStudio).

```{r pressure, echo=FALSE}
data <- read.csv("data_input/combined_data_1.txt", header = FALSE, sep = ",")
data <- data %>% rename(customer_id = V1,
                        rating = V2,
                        date = V3) %>% 
  mutate(date = as.Date(date))
data %>% head()
dim(data)
```

```{r}
data <- data %>% mutate(movie_id = NA)
data
```

```{r}
write.csv(data, "new_data_1.csv")
```



```{r}
data2 <- read.csv("data_input/combined_data_2.txt", header = FALSE, sep = ",")

```


# Data Pre-processing {.tabset}

## Data inspection
```{r}
data_summary <- data %>% 
  group_by(rating)  %>% 
  count(rating)
data_summary
```

```{r}
total_movies <- data.frame(t(colSums(is.na(data))))[1,2]
total_movies
```

```{r}
customers <- nrow(table(unique(data$customer_id)))-total_movies
customers
```


```{r}
levels(data_summary$rating)
```


```{r}
label_percent <- label_dollar(suffix = '%' ,prefix = '')
data_summary <- data_summary %>% mutate(rating = as.factor(rating))
data_summary <- na.omit(data_summary)
data_summary$prob <- data_summary$n/sum(data_summary$n)*100
data_summary <- data_summary %>% 
  mutate(tooltip = glue("distribution: {label_percent(prob)}"))
data_summary
```

# Data Visualization

```{r}
data_sum_graph <- ggplot(data_summary, aes(x = rating, y = prob, text = tooltip, fill = prob)) +
  geom_col(position = "identity") +
  labs(title = "Probability Distribution of Movie Ratings",
       subtitle = paste("For data set 1 (", total_movies, " movies, ", customers, " customers, and ", nrow(data$rating), " ratings"),
       x = "Movie rating",
       y = "Probability") +
  scale_fill_gradient(low = "#e4333e", high = "#52171a") +
  theme_minimal() 
ggplotly(data_sum_graph, tooltip = c("text"))
```

